Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-01-09 Master Thesis/synopsis.tex
Add Hilbert's Irreducibility Theorem

\begin{theorem}[\textit{Hilbert's Irreducibility Theorem}]\label{hilberts-irreducibility-theorem}
Inhalt...
\end{theorem}

>>>>

\begin{theorem}[\textit{Hilbert's Irreducibility Theorem}]\label{hilberts-irreducibility-theorem}
Let $E$ be a number field and $f_1,\ldots, f_n$ be irreducible polynomials in $E[X_1,\ldots,X_r,Y_1,\ldots,Y_s]$. Then there exists $a_1,\ldots,a_r\in E$ such that the specializations
\[ f_1(a_1,\ldots,a_r,Y_1,\ldots,Y_s),\ \ldots,\ f_n(a_1,\ldots,a_r,Y_1,\ldots,Y_s) \]
are irreducible in $E[Y_1,\ldots,Y_s]$.
\end{theorem}
